Inferring Graphics Programs from Images

### 2017-05-17 paper.tex
more writing and rearrangement of figures

We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
These were drawn reasonably carefully but not perfectly.
Because our model assumes that objects are snapped to a $16\times 16$ grid,
we made the drawings on graph paper.
\begin{figure}[H]%
  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/expert-60-reduced.png}
    \subcaption{}
  \end{minipage}%
   \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-groundTruth-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-1-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.2\textwidth}\includegraphics[width = 2cm]{figures/60-2-reduced.png} 
    \subcaption{}
  \end{minipage}
  \caption{(a): a hand drawing. (b): Rendering of the parse our model infers for (a). We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) \& (d) for noisy renderings of (b).}\ref{handDrawingExamples}
\end{figure}

\begin{figure}[H]
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-10.png}
    \includegraphics[width = 2cm]{figures/10-parse.png}    
    \subcaption{Noisy input}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-21.png}
    \includegraphics[width = 2cm]{figures/21-parse.png}    
    \subcaption{A graphical model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-77.png}
    \includegraphics[width = 2cm]{figures/77-parse.png}    
    \subcaption{A figure from a deep learning textbook}
    \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-0.png}
    \includegraphics[width = 2cm]{figures/0-parse.png}    
    \subcaption{Near miss}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-38.png}
    \includegraphics[width = 2cm]{figures/38-parse.png}    
    \subcaption{Failing on a Ising model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-34.png}
    \includegraphics[width = 2cm]{figures/34-parse.png}     
    \subcaption{Illusory contours}
    \end{minipage}
  \caption{Example drawings above model outputs. See also Fig.~\ref{firstPageExamples}}\label{handDrawingExamples}
\end{figure}
For each drawing we annotated a ground truth trace, and evaluated the
model by asking it to sample many candidate traces for each drawing.
For 55\% of the drawings the Top-1 most likely sample matches the
ground truth; as we consider more samples the model encounters traces
that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
\begin{figure}
  \includegraphics[width = 5cm]{figures/drawingAccuracy.png}
  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 10, 100 samples)?
  Distance to the ground truth trace is measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
\end{figure}
Because our current model sometimes makes mistakes on hand drawings,
we envision the current system working as follows:
a user sketches a diagram,
and the system responds by proposing a few candidate interpretations.
The user could then select the one closest to their intention and edit it if necessary.

@@

Why synthesize a graphics program,
if the execution trace already suffices to recover the objects in an image?
Within our domain of hand-drawn figures, graphics program synthesis has several uses:
\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level edits to the figure generated by that program. 
For example,
we can change all of the circles to squares,
were make all of the lines be dashed.
We can also \textbf{extrapolate} figures
by increasing the number of times that loops are executed.

\includegraphics[width = 8in]{figures/extrapolationMatrix.png}
%\input{extrapolations.tex}

>>>>

We drew 100 figures by hand; see figure~\ref{lotsOfHandDrawings}.
These were drawn reasonably carefully but not perfectly.
Because our model assumes that objects are snapped to a $16\times 16$ grid,
we made the drawings on graph paper.
\begin{figure}\centering
  \begin{minipage}{0.45\textwidth}
  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/expert-60-reduced.png}
    \subcaption{}
  \end{minipage}%
   \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-groundTruth-reduced.png}
    \subcaption{}
  \end{minipage}%
  \begin{minipage}[t]{0.3\textwidth}\includegraphics[width = 1.5cm]{figures/60-1-reduced.png}
    \subcaption{}
  \end{minipage}%
    \caption{(a): a hand drawing. (b): Rendering of the trace our model infers for (a). We can generalize to hand drawings like these because we train the model on images corrupted by a noise process designed to resemble the kind of noise introduced by hand drawings - see (c) for a noisy rendering of (b).}\ref{handDrawingExamples}
  \end{minipage}\hfill
  \begin{minipage}{0.45\textwidth}
  \includegraphics[width = 6cm]{figures/drawingAccuracy.png}
  \caption{How close are the model's outputs to the ground truth on hand drawings, as we consider larger sets of samples (1, 5, 10, 100 samples)?
  Distance to the ground truth trace is measured by the intersection over union of predicted vs. ground truth traces (sets of drawing commands).}\label{drawingIntersectionOverUnion}
    \end{minipage}
\end{figure}

\begin{figure}[H]
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-10.png}
    \includegraphics[width = 2cm]{figures/10-parse.png}    
    \subcaption{Noisy input}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-21.png}
    \includegraphics[width = 2cm]{figures/21-parse.png}    
    \subcaption{A graphical model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-77.png}
    \includegraphics[width = 2cm]{figures/77-parse.png}    
    \subcaption{A figure from a deep learning textbook}
    \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-0.png}
    \includegraphics[width = 2cm]{figures/0-parse.png}    
    \subcaption{Near miss}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-38.png}
    \includegraphics[width = 2cm]{figures/38-parse.png}    
    \subcaption{Failing on a Ising model}
  \end{minipage}
  \begin{minipage}[t]{2.25cm}
    \includegraphics[width = 2cm]{figures/expert-34.png}
    \includegraphics[width = 2cm]{figures/34-parse.png}     
    \subcaption{Illusory contours}
    \end{minipage}
  \caption{Example drawings above model outputs. See also Fig.~\ref{firstPageExamples}}\label{handDrawingExamples}
\end{figure}
For each drawing we annotated a ground truth trace, and evaluated the
model by asking it to sample many candidate traces for each drawing.
For 55\% of the drawings the Top-1 most likely sample exactly matches the
ground truth; as we consider more samples the model encounters traces
that are closer to the ground truth annotation (Fig.~\ref{drawingIntersectionOverUnion}).
Because our current model sometimes makes mistakes on hand drawings,
we envision the current system working as follows:
a user sketches a diagram,
and the system responds by proposing a few candidate interpretations.
The user could then select the one closest to their intention and edit it if necessary.

@@

Why synthesize a graphics program,
if the execution trace already suffices to recover the objects in an image?
Within our domain of hand-drawn figures, graphics program synthesis has several uses:
\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level edits to the figure generated by that program. 
For example,
we can change all of the circles to squares,
were make all of the lines be dashed.
We can also \textbf{extrapolate} figures
by increasing the number of times that loops are executed.
Extrapolating repetitive visuals patterns comes naturally to humans,
and building this ability into an application is practical:
imagine hand drawing a repetitive graphical model structure
and having the model automatically induce and extend the pattern.
Fig.~\ref{extrapolationFigure} shows extrapolations of programs synthesized from ground truth traces;
see supplement for our full set of extrapolations.

\begin{figure}
  \includegraphics[width = 8in]{figures/extrapolationMatrix.png}
  \caption{Left: hand drawings. Right: extrapolations produced by
    running different parts of different loops either forward or
    backward an extra iteration.}\label{extrapolationFigure}
  \end{figure}
%\input{extrapolations.tex}
